Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-22 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
more writing in the appendix

The rotating corrections are included using the results of Ref.~\cite{Pierini:2021jxd}, in particular their Eqs.~(51) and~(52),
which for consistency with our previous discussion, we truncated at quartic-order in $\gamma_{\rm EdGB}$.
%
The resulting formula can then be expanded in $\gamma_{\rm EdGB}$ and the coefficients $\delta \omega^{(i)}$ and $\delta \tau^{(i)}$, $i=1,2$
read-off by comparison against Eqs.~\eqref{eq:qnm_nongr_iso}.
%
These steps yield $p_{\rm EdGB} = 4$,
%
\begin{align}
     \delta \omega_{\rm EdGB}^{(0)} = -0.0107, \quad \delta \tau_{\rm EdGB}^{(0)} = -0.2480,
\end{align}
%
for the $j=0$ coefficients and
%
\begin{equation}
    \delta \omega_{\rm EdGB}^{(1)} = -0.2480, \quad \delta \tau_{\rm EdGB}^{(1)} = -1.101.
\end{equation}
%
for the $j=1$ coefficients.

>>>>

The rotating corrections are included using the results of Ref.~\cite{Pierini:2021jxd}, in particular their Eqs.~(51) and~(52),
which for consistency with our previous discussion, we truncated at quartic-order in $\gamma_{\rm EdGB}$.
%
The resulting formula can then be expanded in $\gamma_{\rm EdGB}$ and the coefficients $\delta \omega^{(i)}$ and $\delta \tau^{(i)}$, $i=1,2$
read-off by comparison against Eqs.~\eqref{eq:qnm_nongr_iso}, where for the damping time we use the relation ${\rm Im}(\sigma)_{\rm EdGB} = - 1 / \tau_{\rm EdGB}$
and re-expand in small coupling and spin.
%
These steps yield $p_{\rm EdGB} = 4$,
%
\begin{align}
     \delta \omega_{\rm EdGB}^{(0)} = -0.0107, \quad \delta \tau_{\rm EdGB}^{(0)} = -0.2480,
\end{align}
%
for the $j=0$ coefficients and
%
\begin{equation}
    \delta \omega_{\rm EdGB}^{(1)} = -0.2480, \quad \delta \tau_{\rm EdGB}^{(1)} = -1.101.
\end{equation}
%
for the $j=1$ coefficients.
